# Load data and libraries
```{r}
tuesdata <- tidytuesdayR::tt_load(2021, week = 22)
records <- tuesdata$records
drivers <- tuesdata$drivers
```

```{r}
library(tidyverse)
library(ggrepel)
library(lubridate)
theme_set(theme_light())
```

# Exploration
```{r}
knitr::kable(head(records))
```

## Records by track over time
```{r}
records %>%
	filter(type == "Three Lap") %>%
	filter(shortcut == "No") %>%
	ggplot(aes(x=date, y=time, color=track)) + geom_line() +
	facet_wrap(~ track, scale="free_y") + theme(legend.position="none") +
	#geom_text_repel(aes(label=player)) +
	NULL
```

## Number of record entries by player

```{r}
records %>%
	mutate(player=fct_lump(player,20)) %>%
	mutate(player=fct_rev(fct_infreq(player))) %>%
	ggplot(aes(y=player, fill=shortcut)) + geom_bar() +
	facet_wrap(~type) + scale_fill_brewer(palette="Set1")
```

## How many records have been broken since March 2020?

```{r}
records %>%
	filter(date>ymd('2020-02-29')) %>%
	count(track, sort=T)
```

Only for one track there was no new record since then:
```{r}
tracks_with_new_record <- records %>%
	filter(date>ymd('2020-02-29')) %>%
	pull(track) %>%
	unique
records %>% select(track) %>% unique %>% filter(!(track %in% tracks_with_new_record))
```

Better way to get there is sorting by date:
```{r}
records %>%
	group_by(track) %>%
	top_n(1, date) %>%
	ungroup %>%
	arrange(date)
```

## Answer some of the questions (with plots)

- Which track is the fastest?
- For which track did the world record improve the most?
- For how many tracks have shortcuts been discovered?

### Fastest track (with and without shortcuts)
```{r}
records %>%
	group_by(track, shortcut) %>%
	summarize(record=min(time)) %>%
	ungroup %>%
	mutate(
		nosc_record = if_else(shortcut=="No", record, 0),
		track = fct_reorder(track, nosc_record, max)
	) %>%
	ggplot(aes(y=track, x=record)) +
		geom_col() +
		facet_wrap(~shortcut)
```

There are shortcuts for most tracks (all except 4)
```{r}
records %>%
	group_by(track) %>%
	count(shortcut) %>%
	pivot_wider(names_from=shortcut, values_from=n, values_fill=0) %>%
	filter(Yes==0)
```

### Largest improvement without shortcuts

```{r}


### Number of new records per month

```{r}
records %>%
	mutate(month=floor_date(date, unit="month")) %>%
	count(month) %>%
	arrange(month) %>%
	mutate(cum = cumsum(n)) %>%
	ggplot(aes(x=month, y=cum)) + geom_line()
```
